Red Oak: Proactive Policy Generation

### 2015-05-09 draft.tex
minor changes

type forwarding_decision =
	| Deliver
	| Drop
	| ForwardTo of int
	| Multicast of forwarding_decision
                     l* forwarding_decision

@@

val in_rel: packet -> field list -> relation
    -> bool
\end{lstlisting}

>>>>

type forwarding_decision =
	| Deliver
	| Drop
	| ForwardTo of int
	| Multicast of forwarding_decision
                      * forwarding_decision

@@

val in_rel: packet -> field list -> relation-> bool
\end{lstlisting}
